\plaintitle

### 2017-06-18 papers/IoT2017/prelim.tex
update

%!TEX root = paper.tex
\section{System Model and Requirements}
\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.

>>>>

%!TEX root = paper.tex
\section{System Model and Requirements}

\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
\change{This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.}{The microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder that supports exchange of power between them. Prosumer nodes typically include a smart inverter and a smart meter that controls the flow of power into and out of the prosumer. Additionally, the microgrid contains a set of 
protection nodes that are  responsible for isolating faults on the feeder. Finally, a set of distribution system operator (DSO) controlled switching nodes control the connection of the microgrid to the rest of the distribution system. The Distribution Systems Operator (DSO) is responsible for regulating the net electric power into and out of the microgrid. Starting, from this model we describe the transactive microgrid model in the next section.}
